Reasoning About a Machine with Local Capabilities\\ Provably Safe Stack and Return Pointer Management\\ Technical Appendix Including Proofs and Details

### 2018-04-27 local-capability-machine/local-capability-machine.tex
updated execCond in local capability technical report
typos

\begin{align*}
  & \execCond{}(\gl)(W) = \\
  & \quad
    \begin{aligned}[t]
      \{ \npair{(\perm,\start,\addrend)} \mid &  \forall n' < n \ldotp\\
      & \quad \forall W' \future W \ldotp\\
      & \qquad\forall a \in [\start,\addrend] \ldotp\\
      & \qquad \quad \npair[n']{((\perm,\gl),\start,\addrend,\addr)} \in \stder(W')\}
    \end{aligned} \\
  & \quad \text{where } \gl = \local \Rightarrow \future = \futurewk \\
  & \quad \text{and } \gl = \glob \Rightarrow \future = \futurestr
\end{align*}

@@

\begin{lemma}[$\mathit{execCondition}$ global monotonicity w.r.t $\futurestr$]
  \label{lem:execcond-mono-priv}
  If
  \begin{itemize}
  \item $W' \futurestr W$
  \item $\perm \in \{\exec, \rwx \}$
  \item $\npair{(\perm,\start,\addrend)} \in \execCond{}(\glob)(W)$
  \end{itemize}
  then
  \[
    \npair{(\perm,\start,\addrend)}\in \execCond{}(\glob)(W')
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:execcond-mono-priv}]
  Assume $W_2 \futurestr W_1$, $\perm \in \{\exec, \rwx \}$ and $\npair{(\perm,\start,\addrend)} \in \execCond{}(\glob)(W_1)$. Now let $W_3 \futurestr W_2$, $\addr \in [\start,\addrend]$, and $n' < n$, and show
  \[
    \npair{\stdcap[(\perm,\glob)]} \in \stder(W_3)
  \]
  by transitivity we have $W_3 \futurestr W_1$, so the result follows from $\npair{(\perm,\start,\addrend)} \in \execCond{}(\glob)(W_1)$.
\end{proof}

\begin{lemma}[$\mathit{execCondition}$ downwards-closed]
  \label{lem:execcond-dc}
  If
  \begin{itemize}
  \item $n' \leq n$
  \item $\perm \in \{\exec, \rwx, \rwlx\}$
  \item $\npair{(\perm,\start,\addrend)} \in \execCond{}(\gl)(W)$
  \end{itemize}
  then 
  \[
    \npair[n']{(\perm,\start,\addrend)} \in \execCond{}(\gl)(W)
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:execcond-dc}]
  % TODO
\end{proof}

% EnterCond
\begin{lemma}[$\mathit{enterCondition}$ monotone w.r.t $\futurewk$]
  \label{lem:entrycond-mono-pub}
  If
  \begin{itemize}
  \item $W' \futurewk W$
  \item $\npair{(\addr,\start,\addrend)} \in \entryCond{}(\gl)(W)$
  \end{itemize}
  then
  \[
    \npair{(\addr,\start,\addrend)}\in \entryCond{}(\iota,\gl)(W')
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:entrycond-mono-pub}]
  % TODO
\end{proof}

@@

    \ms'\uplus\ms_r\uplus\ms_f$ and $\heapSat[\ms']{n-i}{W''}$\\

@@

    \ms_{\var{frame}}$ and $\heapSat[P(r)]{n''}{W'(r).H~(W'(r).s)~(\xi^{-1}(W'))}$.

@@

  \item $\heapSat[P(r)]{n''}{W'(r).H~(W'(r).s)~(\xi^{-1}([r\mapsto W'(r)]))}$, i.e.

@@

      public monotonicity and downwards closedness of all islands, and finally

@@

      Lemma~\ref{lem:stdvr-dc}, and teh fact that

@@

      that

@@

      \step[j] \Phi'$ using Lemma~\label{lem:determinacy}.

>>>>

\begin{align*}
  & \execCond{}(\gl)(W) = \\
  & \quad
    \begin{aligned}[t]
      \{ \npair{(\perm,\start,\addrend)} \mid &  \forall n' < n \ldotp\\
      & \quad \forall W' \future W \ldotp\\
      & \qquad\forall a \in [\start',\addrend'] \subseteq [\start,\addrend] \ldotp\\
      & \qquad \quad \npair[n']{((\perm,\gl),\start',\addrend',\addr)} \in \stder(W')\}
    \end{aligned} \\
  & \quad \text{where } \gl = \local \Rightarrow \future = \futurewk \\
  & \quad \text{and } \gl = \glob \Rightarrow \future = \futurestr
\end{align*}

@@

\begin{lemma}[$\mathit{execCondition}$ global monotonicity w.r.t $\futurestr$]
  \label{lem:execcond-mono-priv}
  If
  \begin{itemize}
  \item $W' \futurestr W$
  \item $\perm \in \{\exec, \rwx \}$
  \item $\npair{(\perm,\start,\addrend)} \in \execCond{}(\glob)(W)$
  \end{itemize}
  then
  \[
    \npair{(\perm,\start,\addrend)}\in \execCond{}(\glob)(W')
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:execcond-mono-priv}]
  Assume $W_2 \futurestr W_1$, $\perm \in \{\exec, \rwx \}$ and $\npair{(\perm,\start,\addrend)} \in \execCond{}(\glob)(W_1)$. Now let $W_3 \futurestr W_2$, $\addr \in [\start',\addrend'] \subseteq [\start,\addrend]$, and $n' < n$, and show
  \[
    \npair{((\perm,\glob),\start',\addrend',\addr)} \in \stder(W_3)
  \]
  by transitivity we have $W_3 \futurestr W_1$, so the result follows from $\npair{(\perm,\start,\addrend)} \in \execCond{}(\glob)(W_1)$.
\end{proof}

\begin{lemma}[$\mathit{execCondition}$ downwards-closed]
  \label{lem:execcond-dc}
  If
  \begin{itemize}
  \item $n' \leq n$
  \item $\perm \in \{\exec, \rwx, \rwlx\}$
  \item $\npair{(\perm,\start,\addrend)} \in \execCond{}(\gl)(W)$
  \end{itemize}
  then 
  \[
    \npair[n']{(\perm,\start,\addrend)} \in \execCond{}(\gl)(W)
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:execcond-dc}]
  Follows easily from definition.
\end{proof}

% EnterCond
\begin{lemma}[$\mathit{enterCondition}$ monotone w.r.t $\futurewk$]
  \label{lem:entrycond-mono-pub}
  If
  \begin{itemize}
  \item $W' \futurewk W$
  \item $\npair{(\addr,\start,\addrend)} \in \entryCond{}(\gl)(W)$
  \end{itemize}
  then
  \[
    \npair{(\addr,\start,\addrend)}\in \entryCond{}(\iota,\gl)(W')
  \]
\end{lemma}
\begin{proof}[Proof of Lemma~\ref{lem:entrycond-mono-pub}]
  Follows easily from definition.
\end{proof}

@@

    \ms'\uplus\ms_r\uplus\ms_f$ and $\heapSat[\ms']{n''-i}{W''}$\\

@@

    \ms_{\var{frame}}$ and $\npair[n'']{P(r)} \in W'(r).H~(W'(r).s)~(\xi^{-1}(W'))$.

@@

  \item $\npair[n'']{P(r)} \in W'(r).H~(W'(r).s)~(\xi^{-1}([r\mapsto W'(r)]))$, i.e.

@@

      public monotonicity and downwards closedness of all regions, and finally

@@

      Lemma~\ref{lem:stdvr-dc}, and the fact that

@@

      that\\

@@

      \step[j] \Phi'$ using Lemma~\ref{lem:determinacy}.
